### 2017-03-03 R/ITHIM.Rmd
Removed commented-out lines from ITHIM.Rmd

## R Package _ITHIM_
<!-- This document will eventually serve as a compendium to the R package
_ITHIM_.  It will describe how to use the package to implement the
ITHIM model, as well as a detailed description of the model itself.

As a working document it will serve as a place for SGY to post
results, questions, interpreations, notes, etc.-->

>>>>

## R Package _ITHIM_
